peter_plots

### 2025-01-08 peter_plots.qmd

## 
# Packages
```{r}
library(tidyverse)
library(janitor)
library(ggplot2)
library(scales)
```

# Loading data
```{r}
file_path = "/Users/pdeguz01/Documents/git/Data/2020 CMPS/Output/2020cmps_clean.RData"
load(file_path)
```

# plot 1:
Race and importance of being a member of racial group to identity (Q271)
```{r}

@@

  # Save each plot as a separate image file (optional)
  #ggsave(paste0("plot_", race_value, "Q271.png"), plot = p, width = 6, height = 4)

@@

# plot 2:
Race and interest in politics (Q29)
```{r}
data_summary <- dataset_clean %>%
  group_by(race_recoded, Q29) %>%
  summarise(count = n()) %>%
  mutate(proportion = count / sum(count) * 100)  # Calculate proportion for each race

@@

  # Save each plot as a separate image file (optional)
  #ggsave(paste0("plot_", race_value, "Q29.png"), plot = p, width = 6, height = 4)

@@

# plot 3:
White/Non-White and importance of race to identity (Q271)
```{r}

@@

@@

@@

# plot:
White/Non-White and interest in politics (Q29)
```{r}
data_summary <- dataset_clean %>%
  group_by(white, Q29) %>%
  summarise(count = n()) %>%
  mutate(proportion = count / sum(count) * 100)  # Calculate proportion for each education group

@@

@@

@@

# plot 3:
College Experience and importance of being a member of racial group to identity (Q271)
```{r}
data_summary <- dataset_clean %>%
  group_by(educ, Q271) %>%
  summarise(count = n()) %>%
  mutate(proportion = count / sum(count) * 100)  # Calculate proportion for each education group

plot_collegegrad <- data_summary %>% filter(educ == "College graduate") %>% ggplot(aes(x = Q271, y = proportion, fill = Q271)) +
    geom_bar(stat = "identity", position = "dodge") +
    labs(title = paste("Proportions for Respondents that are College Graduates"), x = "Importance of Race to Identity", y = "Proportion", fill = "Rating") + 
    scale_x_discrete(labels = c("1", "2", "3", "4", "5")) +
    scale_y_continuous(labels = scales::percent_format(scale = 1)) +  # Format y-axis as percentages
    geom_text(aes(label = sprintf("%.0f%%", proportion)),  
              position = position_dodge(width = 0.8),   
              vjust = 1.5,                               
              size = 4,                                  
              color = "white") +   
    theme_minimal() +
    theme(
      axis.text = element_text(size = 12),  # Customize axis text size
      plot.title = element_text(size = 14, hjust = 0.5)  # Center title
    )

@@

plot_somecollege <- data_summary %>% filter(educ == "Some college experience") %>% ggplot(aes(x = Q271, y = proportion, fill = Q271)) +
    geom_bar(stat = "identity", position = "dodge") +
    labs(title = paste("Proportions for Respondents with Some College Experience"), x = "Importance of Race to Identity", y = "Proportion", fill = "Rating") + 
    scale_x_discrete(labels = c("1", "2", "3", "4", "5")) +
    scale_y_continuous(labels = scales::percent_format(scale = 1)) +  # Format y-axis as percentages
    geom_text(aes(label = sprintf("%.0f%%", proportion)),  
              position = position_dodge(width = 0.8),   
              vjust = 1.5,                               
              size = 4,                                  
              color = "white") +  
    theme_minimal() +
    theme(
      axis.text = element_text(size = 12),  # Customize axis text size
      plot.title = element_text(size = 14, hjust = 0.5)  # Center title
    )

print(plot_somecollegeQ271)

plot_nocollege <- data_summary %>% filter(educ == "No college experience") %>% ggplot(aes(x = Q271, y = proportion, fill = Q271)) +
    geom_bar(stat = "identity", position = "dodge") +
    labs(title = paste("Proportions for Respondents with No College Experience"), x = "Importance of Race to Identity", y = "Proportion", fill = "Rating") + 
    scale_x_discrete(labels = c("1", "2", "3", "4", "5")) +
    scale_y_continuous(labels = scales::percent_format(scale = 1)) +  # Format y-axis as percentages
    geom_text(aes(label = sprintf("%.0f%%", proportion)),  
              position = position_dodge(width = 0.8),   
              vjust = 1.5,                               
              size = 4,                                  
              color = "white") +  
    theme_minimal() +
    theme(
      axis.text = element_text(size = 12),  # Customize axis text size
      plot.title = element_text(size = 14, hjust = 0.5)  # Center title
    )

@@

# plot 4:
College Experience and interest in politics (Q29)
```{r}

@@

plot_collegegrad <- data_summary %>% filter(educ == "College graduate") %>% ggplot(aes(x = Q29, y = proportion, fill = Q29)) +
    geom_bar(stat = "identity", position = "dodge") +
    labs(title = paste("Proportions for Respondents that are College Graduates"), x = "Interest in Politics", y = "Proportion", fill = "Rating") + 
    scale_x_discrete(labels = c("1", "2", "3", "4", "5")) +
    scale_y_continuous(labels = scales::percent_format(scale = 1)) +  # Format y-axis as percentages
    geom_text(aes(label = sprintf("%.0f%%", proportion)),  
              position = position_dodge(width = 0.8),   
              vjust = 1.5,                               
              size = 4,                                  
              color = "white") +   
    theme_minimal() +
    theme(
      axis.text = element_text(size = 12),  # Customize axis text size
      plot.title = element_text(size = 14, hjust = 0.5)  # Center title
    )

print(plot_collegegradQ29)

plot_somecollege <- data_summary %>% filter(educ == "Some college experience") %>% ggplot(aes(x = Q29, y = proportion, fill = Q29)) +
    geom_bar(stat = "identity", position = "dodge") +
    labs(title = paste("Proportions for Respondents with Some College Experience"), x = "Interest in Politics", y = "Proportion", fill = "Rating") + 
    scale_x_discrete(labels = c("1", "2", "3", "4", "5")) +
    scale_y_continuous(labels = scales::percent_format(scale = 1)) +  # Format y-axis as percentages
    geom_text(aes(label = sprintf("%.0f%%", proportion)),  
              position = position_dodge(width = 0.8),   
              vjust = 1.5,                               
              size = 4,                                  
              color = "white") +  
    theme_minimal() +
    theme(
      axis.text = element_text(size = 12),  # Customize axis text size
      plot.title = element_text(size = 14, hjust = 0.5)  # Center title
    )

print(plot_somecollegeQ29)

plot_nocollege <- data_summary %>% filter(educ == "No college experience") %>% ggplot(aes(x = Q29, y = proportion, fill = Q29)) +
    geom_bar(stat = "identity", position = "dodge") +
    labs(title = paste("Proportions for Respondents with No College Experience"), x = "Interest in Politics", y = "Proportion", fill = "Rating") + 
    scale_x_discrete(labels = c("1", "2", "3", "4", "5")) +
    scale_y_continuous(labels = scales::percent_format(scale = 1)) +  # Format y-axis as percentages
    geom_text(aes(label = sprintf("%.0f%%", proportion)),  
              position = position_dodge(width = 0.8),   
              vjust = 1.5,                               
              size = 4,                                  
              color = "white") +  
    theme_minimal() +
    theme(
      axis.text = element_text(size = 12),  # Customize axis text size
      plot.title = element_text(size = 14, hjust = 0.5)  # Center title
    )

print(plot_nocollegeQ29)

@@

# plot 4:
Age and importance of being a member of racial group to identity (Q271)
```{r}
data_summary <- dataset_clean %>%
  group_by(S5_AGE, Q271) %>%
  summarise(count = n()) %>%
  mutate(proportion = count / sum(count) * 100)  # Calculate proportion for each race

age_groups <- unique(data_summary$S5_AGE)

# Loop through each age group and generate a plot
for (age_value in age_groups) {
  plot_data <- data_summary %>% filter(S5_AGE == age_value)

@@

  # Save each plot as a separate image file (optional)
  #ggsave(paste0("plot_", age_value, "Q271.png"), plot = p, width = 6, height = 4)

@@

# plot 5:
Age and interest in politics (Q29)
```{r}
data_summary <- dataset_clean %>%
  group_by(S5_AGE, Q29) %>%
  summarise(count = n()) %>%
  mutate(proportion = count / sum(count) * 100)  # Calculate proportion for each race

age_groups <- unique(data_summary$S5_AGE)

# Loop through each age group and generate a plot
for (age_value in age_groups) {
  plot_data <- data_summary %>% filter(S5_AGE == age_value)

@@

  # Save each plot as a separate image file 
  #ggsave(paste0("plot_", age_value, "Q29.png"), plot = p, width = 6, height = 4)

@@

# plot 6:
Rurality and importance of being a member of racial group to identity (Q271)
```{r}
data_summary <- dataset_clean %>%
  group_by(rural, Q271) %>%
  summarise(count = n()) %>%
  mutate(proportion = count / sum(count) * 100)  # Calculate proportion for each race

@@

  # Save each plot as a separate image file 
  #ggsave(paste0("plot_", rural_value, "Q271.png"), plot = p, width = 6, height = 4)

@@

# plot 7:
Rurality and interest in politics (Q29)
```{r}

@@

  # Save each plot as a separate image file 
  #ggsave(paste0("plot_", rural_value, "Q29.png"), plot = p, width = 6, height = 4)

>>>>

##

# Packages

```{r}
library(tidyverse)
library(janitor)
library(ggplot2)
library(scales)
```

# Loading data

```{r}
file_path = "/Users/pdeguz01/Documents/git/Data/2020 CMPS/Output/2020cmps_clean.RData"
load(file_path)
```

# plot 1:

Race and importance of being a member of racial group to identity (Q271)

```{r}

@@

  # Save each plot as a separate image file 
  ggsave(paste0("plot_", race_value, "Q271.png"), plot = p, width = 6, height = 4)

@@

# plot 2:

Race and interest in politics (Q29)

```{r}
data_summary <- dataset_clean %>%
  group_by(race_recoded, Q29) %>%
  summarise(count = n()) %>%
  mutate(proportion = count / sum(count) * 100)  # Calculate proportion for each race

@@

  # Save each plot as a separate image file (optional)
  ggsave(paste0("plot_", race_value, "Q29.png"), plot = p, width = 6, height = 4)

@@

# plot 3:

White/Non-White and importance of race to identity (Q271)

```{r}

@@

ggsave("plot_whiteQ271.png", plot = plot_whiteQ271, width = 6, height = 4)

@@

ggsave("plot_nonwhiteQ271.png", plot = plot_nonwhiteQ271, width = 6, height = 4)

@@

# plot:

White/Non-White and interest in politics (Q29)

```{r}
data_summary <- dataset_clean %>%
  group_by(white, Q29) %>%
  summarise(count = n()) %>%
  mutate(proportion = count / sum(count) * 100)  # Calculate proportion for each education group

@@

ggsave("plot_whiteQ29.png", plot = plot_whiteQ29, width = 6, height = 4)

@@

ggsave("plot_nonwhiteQ29.png", plot = plot_nonwhiteQ29, width = 6, height = 4)

@@

# plot 3:

College Experience and importance of being a member of racial group to identity (Q271)

```{r}
data_summary <- dataset_clean %>%
  group_by(educ, Q271) %>%
  summarise(count = n()) %>%
  mutate(proportion = count / sum(count) * 100)  # Calculate proportion for each education group

plot_collegegradQ271 <- data_summary %>% filter(educ == "College graduate") %>% ggplot(aes(x = Q271, y = proportion, fill = Q271)) +
    geom_bar(stat = "identity", position = "dodge") +
    labs(title = paste("Proportions for Respondents that are College Graduates"), x = "Importance of Race to Identity", y = "Proportion", fill = "Rating") + 
    scale_x_discrete(labels = c("1", "2", "3", "4", "5")) +
    scale_y_continuous(labels = scales::percent_format(scale = 1)) +  # Format y-axis as percentages
    geom_text(aes(label = sprintf("%.0f%%", proportion)),  
              position = position_dodge(width = 0.8),   
              vjust = 1.5,                               
              size = 4,                                  
              color = "white") +   
    theme_minimal() +
    theme(
      axis.text = element_text(size = 12),  # Customize axis text size
      plot.title = element_text(size = 14, hjust = 0.5)  # Center title
    )

ggsave("plot_collegegradQ271.png", plot = plot_collegegradQ271, width = 6, height = 4)

@@

plot_somecollegeQ271 <- data_summary %>% filter(educ == "Some college experience") %>% ggplot(aes(x = Q271, y = proportion, fill = Q271)) +
    geom_bar(stat = "identity", position = "dodge") +
    labs(title = paste("Proportions for Respondents with Some College Experience"), x = "Importance of Race to Identity", y = "Proportion", fill = "Rating") + 
    scale_x_discrete(labels = c("1", "2", "3", "4", "5")) +
    scale_y_continuous(labels = scales::percent_format(scale = 1)) +  # Format y-axis as percentages
    geom_text(aes(label = sprintf("%.0f%%", proportion)),  
              position = position_dodge(width = 0.8),   
              vjust = 1.5,                               
              size = 4,                                  
              color = "white") +  
    theme_minimal() +
    theme(
      axis.text = element_text(size = 12),  # Customize axis text size
      plot.title = element_text(size = 14, hjust = 0.5)  # Center title
    )

ggsave("plot_somecollegeQ271.png", plot = plot_somecollegeQ271, width = 6, height = 4)
print(plot_somecollegeQ271)

plot_nocollegeQ271 <- data_summary %>% filter(educ == "No college experience") %>% ggplot(aes(x = Q271, y = proportion, fill = Q271)) +
    geom_bar(stat = "identity", position = "dodge") +
    labs(title = paste("Proportions for Respondents with No College Experience"), x = "Importance of Race to Identity", y = "Proportion", fill = "Rating") + 
    scale_x_discrete(labels = c("1", "2", "3", "4", "5")) +
    scale_y_continuous(labels = scales::percent_format(scale = 1)) +  # Format y-axis as percentages
    geom_text(aes(label = sprintf("%.0f%%", proportion)),  
              position = position_dodge(width = 0.8),   
              vjust = 1.5,                               
              size = 4,                                  
              color = "white") +  
    theme_minimal() +
    theme(
      axis.text = element_text(size = 12),  # Customize axis text size
      plot.title = element_text(size = 14, hjust = 0.5)  # Center title
    )

ggsave("plot_nocollegeQ271.png", plot = plot_nocollegeQ271, width = 6, height = 4)

@@

# plot 4:

College Experience and interest in politics (Q29)

```{r}

@@

plot_collegegradQ29 <- data_summary %>% filter(educ == "College graduate") %>% ggplot(aes(x = Q29, y = proportion, fill = Q29)) +
    geom_bar(stat = "identity", position = "dodge") +
    labs(title = paste("Proportions for Respondents that are College Graduates"), x = "Interest in Politics", y = "Proportion", fill = "Rating") + 
    scale_x_discrete(labels = c("1", "2", "3", "4", "5")) +
    scale_y_continuous(labels = scales::percent_format(scale = 1)) +  # Format y-axis as percentages
    geom_text(aes(label = sprintf("%.0f%%", proportion)),  
              position = position_dodge(width = 0.8),   
              vjust = 1.5,                               
              size = 4,                                  
              color = "white") +   
    theme_minimal() +
    theme(
      axis.text = element_text(size = 12),  # Customize axis text size
      plot.title = element_text(size = 14, hjust = 0.5)  # Center title
    )

ggsave("plot_collegegradQ29.png", plot = plot_collegegradQ29, width = 6, height = 4)
print(plot_collegegradQ29)

plot_somecollegeQ29 <- data_summary %>% filter(educ == "Some college experience") %>% ggplot(aes(x = Q29, y = proportion, fill = Q29)) +
    geom_bar(stat = "identity", position = "dodge") +
    labs(title = paste("Proportions for Respondents with Some College Experience"), x = "Interest in Politics", y = "Proportion", fill = "Rating") + 
    scale_x_discrete(labels = c("1", "2", "3", "4", "5")) +
    scale_y_continuous(labels = scales::percent_format(scale = 1)) +  # Format y-axis as percentages
    geom_text(aes(label = sprintf("%.0f%%", proportion)),  
              position = position_dodge(width = 0.8),   
              vjust = 1.5,                               
              size = 4,                                  
              color = "white") +  
    theme_minimal() +
    theme(
      axis.text = element_text(size = 12),  # Customize axis text size
      plot.title = element_text(size = 14, hjust = 0.5)  # Center title
    )

ggsave("plot_somecollegeQ29.png", plot = plot_somecollegeQ29, width = 6, height = 4)
print(plot_somecollegeQ29)

plot_nocollegeQ29 <- data_summary %>% filter(educ == "No college experience") %>% ggplot(aes(x = Q29, y = proportion, fill = Q29)) +
    geom_bar(stat = "identity", position = "dodge") +
    labs(title = paste("Proportions for Respondents with No College Experience"), x = "Interest in Politics", y = "Proportion", fill = "Rating") + 
    scale_x_discrete(labels = c("1", "2", "3", "4", "5")) +
    scale_y_continuous(labels = scales::percent_format(scale = 1)) +  # Format y-axis as percentages
    geom_text(aes(label = sprintf("%.0f%%", proportion)),  
              position = position_dodge(width = 0.8),   
              vjust = 1.5,                               
              size = 4,                                  
              color = "white") +  
    theme_minimal() +
    theme(
      axis.text = element_text(size = 12),  # Customize axis text size
      plot.title = element_text(size = 14, hjust = 0.5)  # Center title
    )

ggsave("plot_nocollegeQ29.png", plot = plot_nocollegeQ29, width = 6, height = 4)
print(plot_nocollegeQ29)

@@

# plot 4:

Age and importance of being a member of racial group to identity (Q271)

```{r}
data_summary <- dataset_clean %>%
  group_by(age_recoded, Q271) %>%
  summarise(count = n()) %>%
  mutate(proportion = count / sum(count) * 100)  # Calculate proportion for each race

age_groups <- unique(data_summary$age_recoded)

# Loop through each age group and generate a plot
for (age_value in age_groups) {
  plot_data <- data_summary %>% filter(age_recoded == age_value)

@@

  # Save each plot as a separate image file (optional)
  ggsave(paste0("plot_", age_value, "Q271.png"), plot = p, width = 6, height = 4)

@@

# plot 5:

Age and interest in politics (Q29)

```{r}
data_summary <- dataset_clean %>%
  group_by(age_recoded, Q29) %>%
  summarise(count = n()) %>%
  mutate(proportion = count / sum(count) * 100)  # Calculate proportion for each race

age_groups <- unique(data_summary$age_recoded)

# Loop through each age group and generate a plot
for (age_value in age_groups) {
  plot_data <- data_summary %>% filter(age_recoded == age_value)

@@

  # Save each plot as a separate image file 
  ggsave(paste0("plot_", age_value, "Q29.png"), plot = p, width = 6, height = 4)

@@

# plot 6:

Rurality and importance of being a member of racial group to identity (Q271)

```{r}
data_summary <- dataset_clean %>%
  group_by(rural, Q271) %>%
  summarise(count = n()) %>%
  mutate(proportion = count / sum(count) * 100)  # Calculate proportion for each race

@@

  # Save each plot as a separate image file 
  ggsave(paste0("plot_", rural_value, "Q271.png"), plot = p, width = 6, height = 4)

@@

# plot 7:

Rurality and interest in politics (Q29)

```{r}

@@

  # Save each plot as a separate image file 
  ggsave(paste0("plot_", rural_value, "Q29.png"), plot = p, width = 6, height = 4)
